Parsing mPFC: Community analysis

### 2018-08-28 Manuscript.Rmd
Cleaning up

``` {r Libraries and functions, include = FALSE, fig.align="center", fig.width=6, fig.height=4, echo=FALSE}
Cols <- c("aquamarine4","#D9541A",rgb(190,190,190,100, maxColorValue = 255)) # left, right, interhemisphere

# In case I want to visualize stuff in the brain
labelCoords_vertex <- read.csv2('labelCoords_vertex.csv', sep = ",")[,2:6]
labelCoords_vertex <- transform(labelCoords_vertex, x = as.numeric(as.character(x)), y = as.numeric(as.character(y)), z = as.numeric(as.character(z)))

@@

``` {r For HCP data, fig.align="center", echo=FALSE, message = FALSE}
setwd('./For_HCP')
temp <- list.files(pattern = '*Binary*')
FB <- lapply(temp, read.table)
Summed <- do.call(cbind, lapply(FB, "[[", 'V1')) - 1
FB_Means <- rowMeans(Summed)

write.table(file = 'propDMN_all.txt', FB_Means, row.names = F, col.names = F, dec = ".")
```

## Notes:

  - The mixed effects GLM is not that well defined. Fix the dependent to include total possible and actuals.
  - If we stick to the linear model, maybe plot the day and subject coefficients for PCC and PFC too (all in onw plot).
  - The official manuscript will probably have to include things like community size, density of each subject's network (so far, ~0.65), and maybe clustering coefficient?

@@

## Methods
Tentative outline:

- Meta-analysis
- fMRI data
- Network definition
- Community detection
- Evaluation

@@

**Within-ROI Connectivity**
For the third stage, I “zoomed in” each subject’s brain by computing the correlation among all of the surface-vertices contained within each ROI across all the ROIs, and applied the same correction as in step two. That means that the vertices became smaller functional brain units that are connected by the same type of edge (i.e. adjusted correlations) as in step two. This time, I only focused on partitioning the brain through modularity and spectral partitioning to see if the ROIs can be subdivided at this finer level of resolution. It is worth noting that while communities across subjects should be similar, the idiosyncrasies explained previously (i.e. cortical folding) should produce noticeable differences as well.

@@

>>>>

``` {r Libraries and functions, include = FALSE, fig.align="center", fig.width=6, fig.height=4, echo=FALSE}

Cols <- c("aquamarine4","#D9541A",rgb(190,190,190,100, maxColorValue = 255)) # left, right, interhemisphere

# In case I want to visualize stuff in the brain
labelCoords_vertex <- read.csv2('labelCoords_vertex.csv')[,2:6]
labelCoords_vertex <- transform(labelCoords_vertex, x = as.numeric(as.character(x)), y = as.numeric(as.character(y)), z = as.numeric(as.character(z)))

@@

``` {r For HCP data, fig.align="center", echo=FALSE, message = FALSE}
# setwd('./For_HCP')
# temp <- list.files(pattern = '*Binary*')
# FB <- lapply(temp, read.table)
# Summed <- do.call(cbind, lapply(FB, "[[", 'V1')) - 1
# FB_Means <- rowMeans(Summed)
# 
# write.table(file = 'propDMN_all.txt', FB_Means, row.names = F, col.names = F, dec = ".")
```

@@

## Methods

@@

For the third stage, I “zoomed in” each subject’s brain by computing the correlation among all of the surface-vertices contained within each ROI across all the ROIs, and applied the same correction as in step two. That means that the vertices became smaller functional brain units that are connected by the same type of edge (i.e. adjusted correlations) as in step two. This time, I only focused on partitioning the brain through modularity and spectral partitioning to see if the ROIs can be subdivided at this finer level of resolution. It is worth noting that while communities across subjects should be similar, the idiosyncrasies explained previously (i.e. cortical folding) should produce noticeable differences as well.

@@

**Community Detection**

**Evaluation**
